D3064R0: OOTA Execution on Real Implementations is Provably Vacuous

### 2023-12-19 ootavacuous.tex
Reference Appendix instead of Retrocausality URL
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Plato's ``Timaeus'' notwithstanding, there has been much recent debate
as to whether the universe is in fact causal with cause necessarily
preceding effect.
However, no one has managed to construct a real time-travel machine
or any other apparatus that might result in effect preceding cause,
as discussed at length in the Wikipedia article on retrocausality and
its many references.\footnote{
	\url{https://en.wikipedia.org/wiki/Retrocausality}.}

>>>>

Plato's ``Timaeus'' notwithstanding, there has been much recent debate
as to whether the universe is in fact causal with cause necessarily
preceding effect.
However, no one has managed to construct a real time-travel machine
or any other apparatus that might result in effect preceding cause,
as discussed at length in Appendix~\ref{sec:Debates on Causality} and 
the URL that it provides.
